---
title: "R Graphics Cookbook Chapter 5"
author: "NAME"
date: "`r Sys.Date()`"
output: html_document
---

### Chapter 5. Scatter Plots

```{r}
library(ggplot2)
library(gcookbook)
```

### Section 5.1. Making a Basic Scatterplot

```{r}
 
```

### Section 5.2. Grouping Data Points by a Variable Using Shape or Color

```{r}

```

### Section 5.3. Using Different Point Shapes

```{r}

```

### Section 5.4. Mapping a Continuous Variable to Color or Size

```{r}
 
```

### Section 5.5 Dealing with Overplotting

```{r}

```

### Section 5.6. Adding Fitted Regression Model Lines

```{r}

```

### Section 5.7. Adding Fitted Lines from an Existing Model

```{r}

```

### Section 5.8. Adding Fitted Lines from Multiple Existing Models

```{r}

```

### Section 5.9. Adding Annotations with Model Coefficients

```{r}

```

### Section 5.10. Adding Marginal Rugs to a Scatterplot

```{r}

```

### Section 5.11. Labeling Point in a Scatterplot

```{r}

```

### Section 5.12. Creating a Balloon Plot

```{r}

```

### Section 5.13. Making a Scatterplot Matrix

```{r}

```


<hr>
END!