---
title: "R Graphics Cookbook Chapter 13"
author: "NAME"
date: "`r Sys.Date()`"
output: html_document
---

### Chapter 13. Miscellaneous Graphs

```{r}
library(ggplot2)
library(gcookbook)
```

### Section 13.1. Making a Correlation Matrix

```{r}
 
```

### Section 13.2. Plotting a Function

```{r}

```

### Section 13.3. Shading a Subregion Under a Function Curve

```{r}

```

### Section 13.4. Creating a Network Graph

```{r}
 
```

### Section 13.5. Using Text Labels in a Network Graph

```{r}

```

### Section 13.6. Creating a Heat Map

```{r}

```

### Section 13.7. Creating a Three-Dimensional Scatter Plot

```{r}

```

### Section 13.8. Adding a Prediction Surface to a Three-Dimensional Plot

```{r}

```

### Section 13.9. Saving a Three-Dimensional Plot

```{r}

```

### Section 13.10. Animating a Three-Dimensional Plot

```{r}

```

### Section 13.11. Creating a Dendrogram

```{r}

```

### Section 13.12. Creating a Vector Field

```{r}

```

### Section 13.13. Creating a QQ Plot

```{r}

```

### Section 13.14. Creating a Plot of an Empirical Cumulative Distribution Function

```{r}

```

### Section 13.15. Creating a Mosaic Plot

```{r}

```

### Section 13.16. Creating a Pie Chart

```{r}

```

### Section 13.17. Creating a Map

```{r}

```

### Section 13.18. Creating a Chloropleth Map

```{r}

```

### Section 13.19. Making a Map with a Clean Background

```{r}

```

### Section 13.20. Rceating a Map from a Shapefile

```{r}

```


<hr>
END!