---
title: "R Graphics Cookbook Chapter 8"
author: "NAME"
date: "`r Sys.Date()`"
output: html_document
---

### Chapter 8. Axes

```{r}
library(ggplot2)
library(gcookbook)
```

### Section 8.1. Swapping X- and Y- Axes

```{r}
 
```

### Section 8.2. Setting the Range of a Continuous Axis

```{r}

```

### Section 8.3. Reversing a Continuous Axis

```{r}

```

### Section 8.4. Changing the Order of Items on a Categorial Axis

```{r}
 
```

### Section 8.5. Setting the the Scaling Ratio of the X- and Y-Axes

```{r}

```

### Section 8.6. Setting the Position of Tick Marks

```{r}

```

### Section 8.7. Removing Tick Marks and Labels

```{r}

```

### Section 8.8. Changing the Text of Tick Labels

```{r}

```

### Section 8.9. Changing the Appearance of Tick Labels

```{r}

```

### Section 8.10. Changing the Text of Axis Labels

```{r}

```

### Section 8.11. Removing Axis Labels

```{r}

```

### Section 8.12. Changing the Appearance of Axis Labels

```{r}

```

### Section 8.13. Showing Lines Along the Axis

```{r}

```

### Section 8.14. Using a Logarhithmic Axis

```{r}

```

### Section 8.15. Adding Ticks for a Logarhithmic Axis

```{r}

```

### Section 8.16. Making a Circular Graph

```{r}

```

### Section 8.17. Using Dates on an Axis

```{r}

```

### Section 8.18. Using Relative Times on an Axis

```{r}

```


<hr>
END!